---
title: "Predict Gas Guzzlers using a Neural Net Model on the MPG Data Set"
author: "Priya"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

Loading libraries needed
```{r}
library(neuralnet)

```


Create a Data Frame
We will use the dataset mtcars.
We're going to create a new variable called mpg2.  If the car has greater than 22 mpg that it's a one.  If less than 0.  This creates a binary variable, which we can use in the NN.

```{r}
hist(mtcars$mpg)
mtcars$mpg2 <- ifelse(mtcars$mpg > 22,1,0)
data <- mtcars
rows <- sample(1:nrow(data), nrow(data) * .7, replace = F)
train <- data[rows,]
test <- data[-rows,]
```

Creating a neural net model
We are going to use all the variables. It is also a logistic neural net model.

```{r}
set.seed(222)
model <- neuralnet(mpg2 ~ ., train,
                  act.fct = "logistic", linear.output = F )
?neuralnet
```

We can also plot the model to see the structure of neuralnet

```{r}
plot(model)
```


Testing the model
We call the compute method to test the model on our test set.


```{r}

predict <- neuralnet::compute(model, test)
predict
```

Creating Confusion matrix

```{r}
results <- ifelse(predict$net.result > .5, 1,0)

table(results, test$mpg2)
```

